District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa

### 2023-08-09 paper/paper.tex
Add paper and supplementary figures drafts in TeX from Matt

@@

\section{Methods}
\label{sec:orga131cc6}

@@

>>>>

\vspace{-1cm}

Patrick O'Toole\textsuperscript{1},
Matthew L. Thomas\textsuperscript{1,2},
Oliver Stevens\textsuperscript{1},
Kevin Lam\textsuperscript{1,3},
Katharine Kripke\textsuperscript{4},
Rachel Esra\textsuperscript{1},
Ian Wanyeki\textsuperscript{5},
Lycias Zembe\textsuperscript{5},
Jeffrey W. Eaton\textsuperscript{1,6} \\
\smallskip

\textbf{1} MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial Colleg  e London, London, United Kingdom\\
\textbf{2} Department of Earth and Environmental Sciences, University of Manchester, Manchester, United Kingdom\\
\textbf{3} Department of Statistics, University of British Columbia, Vancouver, Canada\\
\textbf{4} Avenir Health, Washington, District of Columbia, United States of America\\
\textbf{5} Joint United Nations Programme on HIV/AIDS (UNAIDS), Geneva, Switzerland\\
\textbf{6} Center for Communicable Disease Dynamics, Department of Epidemiology, Harvard T.H. Chan School of Public Health, Boston, Massachusetts, United States of America\\

\smallskip

* Corresponding Author Email

@@

\section{Introduction}

HIV epidemic continues to to be a problem. Many interventions available etc. VMMC has been proven to be an effective way of doing this.

The World Health Organization (WHO) and the Joint United Nations Programme on HIV/AIDS (UNAIDS) have identified fifteen countries in sub-Saharan Africa that have a high HIV prevalence and low male circumcision (MC) coverage as priority countries which should scale-up VMMC for HIV prevention: Botswana, Eswatini, Ethiopia, Kenya, Lesotho, Malawi, Mozambique, Namibia, Rwanda, South Africa, South Sudan Tanzania, Uganda, Zambia, and Zimbabwe \todo{Check this and the citations} \cite{UNAIDSJoint, davis2018progress, WHOVoluntary2}. Since 2007, there have been XX\todo{Find this number and cite} million VMMCs conducted in these countries with the support of national governments as well as international organisations such as US President’s Emergency Plan for AIDS Relief (PEPFAR) and the Global Fund to Fight AIDS, Tuberculosis and Malaria. Targets were set by UNAIDS to reach 80\% circumcision coverage among men aged 15--49 years in priority countries by 2015 which have since been updated to reach 90\% circumcision coverage among adolescent boys and young men aged 10--29 years by 2021 \cite{WHOFramework}.

The landscape of male circumcision in sub-Saharan Africa is complex and highly heterogeneous. Despite the upscaling in medical male circumcision (MMC) being a recent phenomenon, it has been long been practised as part of traditional male initiation ceremonies in many African countries. The provision of traditional male circumcision (TMC), such as the typical age at circumcision and what it entails, can vary considerably and is influenced by community, religious, ethnic and cultural led values. There is substantial sub-national heterogeneity in the proportion and average of men receiving TMC between at a district level in South Africa. Even on a national level TMC is universally practiced in {\color{red}\bf XXX} and is barely conducted in {\color{red}\bf XXX}. TMCs conducted during male initiation ceremonies are often performed using non-medical methods non-clinical settings by a traditional practitioner with no formal medical training. The evidence that TMC provides the same HIV prevention benefits as MMC is mixed, due to TMC may not involve a complete circumcision and instead be only partial removal of the foreskin or a simple incision in the prepuce in some populations.  \todo{Cite this paragraph.}

Why is understanding this important? DMPPT2 and Cork et al. and Thomas et al. have been approaches

In this paper,...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Methods}
\label{sec:orga131cc6}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
